Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-18 src/article.tex
replace nums with cites

In this context, a `traditional' instrument is one whose interface for
generating sound and the sound generating mechanism are fundamentally
coupled. A piano requires a key press which triggers a hammer, which
strikes a string which vibrates a body and air cavity. This system is
tied together and cannot be separated. A synthesizer, be it a theremin,
a control voltage synthesizer, a MIDI controller, these are all
instruments whose interface are decoupled from their sound generation.
This decoupling presents a problem that then needs to be addressed. How
do we re-introduce this dimension to the experience of playing a musical
instrument? How do we, and is it possible to, parameterise and preserve
this experience? This is central problem that is trying to be solved in
{[}1, 2{]}.

@@

\subsection{Example Trasuntino}\label{example-trasuntino}

\begin{itemize}
\item
  {[}1538{]}
  https://carmentis.kmkg-mrah.be:443/eMP/eMuseumPlus?service=ExternalInterface\&module=collection\&objectId=106088\&viewType=detailView
\item
  {[}1531{]}https://museumcollections.rcm.ac.uk/collection/Details/collect/58
\end{itemize}

>>>>

In this context, a `traditional' instrument is one whose interface for
generating sound and the sound generating mechanism are fundamentally
coupled. A piano requires a key press which triggers a hammer, which
strikes a string which vibrates a body and air cavity. This system is
tied together and cannot be separated. A synthesizer, be it a theremin,
a control voltage synthesizer, a MIDI controller, these are all
instruments whose interface are decoupled from their sound generation.
This decoupling presents a problem that then needs to be addressed. How
do we re-introduce this dimension to the experience of playing a musical
instrument? How do we, and is it possible to, parameterise and preserve
this experience? This is central problem that is trying to be solved in
\cite{Nichols2002, Timmermans2020, McAlpine2014, Baldwin2016}.

@@
